Notebook with AMP-AD RNA-seq network analysis results

### 2020-01-03 manuscript.Rmd
compare modules

Build aggregate modules from individual modules and differential expression meta-analysis, this will give you the same modules as are stored at syn11932957

```{r}
synapser::synLogin()

@@

>>>>

Build aggregate modules from individual modules and differential expression meta-analysis, this will give you the same modules as are stored at syn11932957 - this code block builds the aggregate modules, and then checks if they are different from the paper aggregate modules.

```{r}
synapser::synLogin()
aggModsNew <- AMPAD::buildAggregateModules()
aggModsPaper <- synapser::synTableQuery('select * from syn11932957')$asDataFrame()[,-c(1,2)]

sum(aggModsNew[,1]!=aggModsPaper[,1])
sum(aggModsNew[,2]!=aggModsPaper[,2])
```

Make the pairwise enrichment plot (Figure 1B)

```{r}
synapser::synLogin()
AMPAD::pairwiseMatrixOfEnrichments('syn11932957')
```

Build aggregate modules without restricting the aggregation operation to the individual modules that are enriched for differentially expressed genes in AD.

```{r}
synapser::synLogin()
aggModsNonAdNew <- AMPAD::buildAggregateNonADModules()

@@

Show overlap between AD and non AD (Figure SXF)
```{r}
AMPAD::compareADtoNonADmods(aggModsNew,
                            aggModsNonAdNew)
